---
title: "mixcuref.cr Manual"
author: "Changchang Xu"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{mixcuref.cr Manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

# Overview

`mixcuref.cr` computes bivariate confidence regions for Weibull proportional-hazards mixture cure models. The package focuses on profile-likelihood confidence regions (PLCR), Wald-type confidence regions, region plotting, and area calculations.

The main functions are:

- `mixcure.penal.polar.plcr()` for PLCR edge-point estimation by the radial-angular method
- `plot.mixcure.penal.polar.plcr()` for plotting PLCR or Wald regions
- `mixcure.penal.plcr.area()` for area calculation of a PLCR
- `mixcure.penal.wald.cr.area()` for area calculation of a Wald-type region
- `mixcure.penal.profile.point()` for one-dimensional profile-likelihood point calculations
- `plcr.surface()` for surface exploration
- `mixcurefcr_fit()` as the adapter used by `Mixcuref.Meta`

# Package data

The package includes:

- `ANNbcBMdat1`
- `ANNbcBMdat2`
- `ANNbcBMdat5`

These datasets represent breast cancer recurrence settings with different event rates and model complexity.

# PLCR estimation

```{r}
library(mixcuref.cr)
library(survival)

data(ANNbcBMdat5)

plcr_obj <- mixcure.penal.polar.plcr(
  Surv(Time, CENS == 1) ~ Her2 + LuminalA + TN + MENS0 + TUMCT,
  data = ANNbcBMdat5,
  apct = 0.05,
  init = c(5, rep(0, 5), -10, rep(0, 5), 0.1),
  pl = FALSE
)

head(plcr_obj$plcr)
plcr_obj$coefficients
```

# Plotting the confidence region

```{r}
plot.mixcure.penal.polar.plcr(
  obj_cr = plcr_obj,
  cr_type = "PLCR",
  title_name = "PLCR for ANNbcBMdat5"
)
```

A Wald-type region can be requested by changing `cr_type = "Wald"`.

```{r}
plot.mixcure.penal.polar.plcr(
  obj_cr = plcr_obj,
  cr_type = "Wald",
  title_name = "Wald CR for ANNbcBMdat5"
)
```

# Region area

```{r}
plcr_area <- mixcure.penal.plcr.area(plcr_obj)
plcr_area
```

```{r}
wald_area <- mixcure.penal.wald.cr.area(
  formula = Surv(Time, CENS == 1) ~ Her2 + LuminalA + TN + MENS0 + TUMCT,
  data = ANNbcBMdat5,
  apct = 0.05,
  init = c(5, rep(0, 5), -10, rep(0, 5), 0.1),
  true.val = NULL,
  pl = FALSE
)
wald_area
```

# Profile-likelihood points and surfaces

```{r}
prof_pt <- mixcure.penal.profile.point(
  formula = Surv(Time, CENS == 1) ~ Her2 + LuminalA + TN + MENS0 + TUMCT,
  data = ANNbcBMdat5,
  init = c(5, rep(0, 5), -10, rep(0, 5), 0.1),
  k = 2,
  kval = 0,
  pl = FALSE
)
prof_pt
```

```{r}
plcr.surface(
  formula = Surv(Time, CENS == 1) ~ Her2 + LuminalA + TN + MENS0 + TUMCT,
  covar = "Her2",
  indata = ANNbcBMdat5,
  init = c(5, rep(0, 5), -10, rep(0, 5), 0.1),
  pl = FALSE
)
```

# Meta-layer adapter

`mixcuref.cr` can also be called through `Mixcuref.Meta`.

```{r}
# spec is a model specification object created by Mixcuref.Meta
# fit <- mixcurefcr_fit(spec, control = list(apct = 0.05, pl = FALSE))
```

# Notes

- `pl = FALSE` requests the usual likelihood.
- `pl = TRUE` requests Firth-type penalized likelihood.
- The initialization vector follows the same convention as `mixcuref`.
- The object returned by `mixcure.penal.polar.plcr()` contains edge points in `obj$plcr` and coefficient summaries in `obj$coefficients`.

# Session information

```{r, eval=T, echo=F}
pkgs <- c(
#  "mixcuref.cr",
  "survival",
  "ggplot2",
  "ellipse",
  "reshape2",
  "dplyr",
  "tidyr",
  "purrr"
)

desc_field <- function(pkg, field) {
  x <- tryCatch(utils::packageDescription(pkg, fields = field), error = function(e) NA)
  if (is.null(x) || is.na(x)) "" else x
}

pkg_table <- data.frame(
  Package = pkgs,
  Version = sapply(pkgs, function(x) as.character(packageVersion(x))),
  Built   = sapply(pkgs, desc_field, field = "Built"),
  Remote  = sapply(pkgs, desc_field, field = "RemoteSha"),
  row.names = NULL,
  stringsAsFactors = FALSE
)

knitr::kable(pkg_table, caption = "Package Versions")

cat("\n\n")

#sessionInfo()
```
